A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2012-05-18 paper/paper.tex
Added bibliography from old paper to new paper.

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath}               % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments

@@

\title{Diameter and Pinched Sphere Theorems for Positively Curved Combinatorial 3-Manifolds}

@@

\begin{abstract}
  Blah blah...
\end{abstract}

@@

@@

>>>>

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath}               % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments
\usepackage{url}

@@

\title{A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds}

@@

\begin{abstract}
  This paper presents a discrete version of Grove and Shiohama's generalized sphere theorem.
\end{abstract}

@@

\begin{thm}[Grove-Shiohama] Let $M$ be a complete, connected, $n$-dimensional Riemannian manifold with section curvature $K \geq \delta > 0$ and $diam(M) > \frac{\pi}{2\sqrt{\delta}}$. Then, $M$ is homeomorphic to a sphere.
\end{thm}

@@

\begin{thebibliography}{99}

    \bibitem{BMM}N. Brady, J. McCammond, and J. Meier, {\em Bounding edge degrees in triangulated 3-manifolds}, Proc. Amer. Math. Soc. 132 (2004), no. 1, 291--298 (electronic).

    \bibitem{cheng}Y. Cheng, {\em Eigenvalue comparison theorems and its [sic] geometric applications}, Math. Z. 143 (1975) 289-297.

    \bibitem{Crowley}K. Crowley, Doctoral Thesis (Rice University), {\em Discrete Morse Theory and the Geometry of Nonpositively Curved Simplicial Complexes}. (2001).

    \bibitem{EMM}M. Elder, J. McCammond, and J. Meier, {\em Combinatorial conditions that imply word-hyperbolicity for 3-manifolds.}, Topology, 42, (2003), 1241-1259.

    \bibitem{forman1}R. Forman, {\em Morse theory for cell complexes}, Adv. in Math. 134 (1998), 90-145.

    \bibitem{forman2}R. Forman, {\em Combinatorial Differential Topology and Geometry}, New perspectives in algebraic combinatorics (Berkeley, CA, 1996--97), 177--206, Math. Sci. Res. Inst. Publ., 38, Cambridge Univ. Press, Cambridge, 1999.

    \bibitem{GGL}A. Gabrielov, I. Gelfand, and M. Losik.  {\em Combinatorial computation of characteristic classes}. I, II, and {\em A local combinatorial formula for the first Pontrjagin class}. Functional Anal. Appl. 9 (1975), no. 2, 103--116; ibid. 9 (1975), no. 3, 186--202 (1976); ibid. 10 (1976), no. 1, 12--15.

    \bibitem{groveshiohama}K. Grove; K, Shiohama, {\em A generalized sphere theorem}, Ann. of Math. 106 (1977), 201-211.

    \bibitem{gromov}M. Gromov, {\em Curvature, diameter, and Betti numbers}, Comm. Math. Helvetici 56 (1981), 179-195.

    \bibitem{LS}F. Luo and R. Stong, {\em Combinatorics of triangulations of 3-manifolds.} Trans. Amer. Math. Soc. 337 (1993), no. 2, 891-906.

    \bibitem{stone}D.A. Stone, {\em Sectional curvature in piecewise linear manifolds}, Bull. Amer. Math. Soc., vol. 79 (1973), pp. 1060-1063.

    \bibitem{toponogov}V.A. Toponogov, {\em Riemannian spaces having their curvature bounded below by a positive number}, Uspekhi Math. Nauk 14 (1959), 87-135 English Translation: Amer. Math. Soc.Transl. Ser. 37 (1964) 287-290.

    \bibitem{DDS} M. Deza, M. Dutour and M. Shtogrin, {\em On simplicial and cubical complexes with short links}, Israel Journal of Mathematics 144 (2004) 109-
124.

    \bibitem{LutzSul} F. H. Lutz and J. M. Sullivan: {\em Simplicial manifolds with small valences}.
In preparation.

\end{thebibliography}
